### 2019-05-24 7_conclusion.tex
Add other systems to conclusion.

>>>>

We have implemented Task Bench for a broad set of programming systems
spanning large scale data analytics and HPC. However, there are
systems not represented in our evaluation that would be interesting to
consider in the future. These include GASNet~\cite{GASNET07},
Habanero~\cite{Habanero11}, Hadoop~\cite{Hadoop},
HPX~\cite{Kaiser2014}, Nimbus~\cite{Nimbus17}, OCR~\cite{OCR14},
OpenSHMEM~\cite{OpenSHMEM10}, Ray~\cite{Ray18}, and UPC~\cite{UPC99}.
